---
title: "Alcohol vs Seat choice"
author: "Daryl Perry"
date: "AUG 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
The median shows that 5 drinks is the amount of alchol consumed by those who sat at the back compared to those who sat in the middle which was about 3 drink and those that sat in the front which was about 1 drinks.  
# Numerical results
```{r}
favstats(davisdata~Seat,data=davisdata)
```


```{r}
favstats(alcohol~Seat,data=davisdata)
```


## Numerical Summarys 
the data clearly shows the median for the back row is rated 4 and the median for the front is 0 and 1 for those in the middle seats.Tthe mean values for the three samples are back-9.625000, Front-1.803030 Middle-3.283133

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
the inferential data provided the data with information concerning the probability of p-value being 0.000116 which declares a one in 10,000 chance of there being no difference in the seating arrangement  having no influence on Alcohol Consumption

## Conclusions

with the return of Numerical, and Inferential, Data in the form of plots,and one way anova it is clear that there is no possible chance of the null hypothesis can be True, do to the 6 digit decimal number expressing the possibility of of change , So I reject it.
