---
title: "Alcohol vs Seat choice"
author: "Daryl Perry"
date: "Fall 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
The median shows that 5 drinks is the amount of alchol consumed by those who sat at the back compared to those who sat in the middle which was about 3 drink and those that sat in the front which was about 1 drinks.  
# Numerical results



```{r}
favstats(alcohol~Seat,data=davisdata)
```
```

## Numerical Summarys 
the data clearly shows the median for the back row is rated 4 and the median for the front is 0 and 1 for those in the middle seats

## Inferential Tests

## Conclusions


